---
title: "Linear Optimization Using R"
author: "Abhay Padda"
date: "8 February 2018"
output:
  word_document: default
  html_document: default
---
# Linear Optimization Problem
#### A company wants to maximize the profit for two products A and B which are sold at $ 25 and $ 20 respectively. There are 1800 resource units available every day and product A requires 20 units while B requires 12 units. Both of these products require a production time of 4 minutes and total available working hours are 8 in a day. What should be the production quantity for each of the products to maximize profits.

### The objective function in the above problem will be:

#### max(Sales) = max(25 x1 + 20 x2)

#### where,
#### x1 is the units of Product A produced
#### x2 is the units of Product B produced
#### x1 and x2 are also called the decision variables

### The constraints (resource and time) in the problem:

#### 20x1 + 12 x2 <= 1800 (Resource Constraint)
#### 4x1 + 4x2 <= 8*60 (Time constraint)
```{r}
## Load the package lpsolve
library(lpSolve)

## Set the coefficients of the decision variables
objective.in  <- c(25,  20)

## Create constraint martix
const.mat <- matrix(c(20,  12,  4,  4),  nrow=2, byrow=TRUE)

## define constraints
time_constraint <- (8*60)
resource_constraint <- 1800

## RHS for the constraints
const.rhs <- c(resource_constraint, time_constraint)

## Constraints direction
const.dir  <- c("<=",  "<=")

## Find the optimal solution
optimum <-  lp(direction="max",  objective.in, const.mat, const.dir,  const.rhs)
```

```{r}
## Display the optimum values for x1 and x2
optimum$solution

## Check the value of objective function at optimal point
optimum$objval

```

#### From the above output, we can see that the company should produce 45 units of Product A and 75 units of Product B to get sales of $2625, which is the maximum sales that company can get given the constraints.

